Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-26 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Purpose of graph

We argue also
that a graph model is a viable representation for this purpose,  % define better the purpose. Not clear. "giving the same importance to users and their interactions"? - JJ
% I was thinking to record all the activities and relationships

presenting a natural way of mapping the relationships found in the system. 
Most IEAs have % have is not very precise and I'm a bit lost
               % here. What do you mean? is this constrained to IEAs
               % or EAs? At least the first is not exclusive, right? - JJ
the following many-to-many relations:

>>>>

We argue also
%that a graph model is a viable representation for this purpose,  % define better the purpose. Not clear. "giving the same importance to users and their interactions"? - JJ
% I was thinking to record all the activities and relationships
that a graph model is a viable representation for the above relationships and
interactions. Graph based models are currently used in social networks to keep track
of user interactions with media objects, places, and other users. Users of
social networks (for instance the Facebook Graph) are accustomed to express these 
complex relationships for instance: ``Jhon and Ann eating breakfast at Tony's''. 
Other example is the W3C Activity Streams 2.0 specification used for representing activities 
common in social web applications.

%presenting a natural way of mapping the relationships found in the system. 
Most IEAs have % have is not very precise and I'm a bit lost
               % here. What do you mean? is this constrained to IEAs
               % or EAs? At least the first is not exclusive, right? - JJ
the following many-to-many relations:
